\documentclass[11pt,a4paper]{article}
\usepackage[margin=1.7cm]{geometry}
\usepackage{fontspec}
\IfFontExistsTF{Source Sans 3}{
  \setmainfont{Source Sans 3}
}{
  \setmainfont{Times New Roman}
}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}

\begin{document}

{\LARGE \textbf{Cristi Prodan}}\\
Phone: +40 746 708 927 \\
Email: \href{mailto:prodan.cristian@gmail.com}{prodan.cristian@gmail.com} \\
GitHub: \href{https://github.com/christian}{https://github.com/christian} \\
LinkedIn: \href{https://www.linkedin.com/in/cristianprodan/}{https://www.linkedin.com/in/cristianprodan/}

\section*{Summary}
Senior Software Engineer with experience designing and building cloud-based systems, microservices, and API platforms. Focused on reliability, scalability, and delivering production-ready software. Experienced across the stack, from DevOps to frontend, with particular strength in backend engineering. Recently developed an MVP end-to-end and enjoy working autonomously while collaborating with cross-functional teams.

\section*{Experience}
\subsection*{Independent contractor (Remote EU - Romania) \hfill Jan 2025 - Feb 2026}
\begin{itemize}
  \item Transitioned into independent contracting to explore diverse projects and clients.
  \item Founded and bootstrapped an e-commerce platform MVP that enables entrepreneurs to create and manage online stores; launched at \href{https://comerz.ro/}{comerz.ro}.
  \item multitenant, Rails, Postgresql.
  \item Enjoyed generative AI capabilities: codex, conductor, linear.
\end{itemize}

\subsection*{Senior Software Engineer, Zerofy (Remote EU - Romania) \hfill Jan 2024 - Feb 2025}
\begin{itemize}
  \item Built serverless event-driven workflows with Google Cloud Functions (lambda), Firebase, Node.js (cloud-native on GCP) to support the mobile frontend (Zerofy App LIVE).
  \item Integrated external vendor APIs, including reverse-engineered interfaces when documentation was unavailable.
  \item Reduced technical debt through targeted refactors and cleanup.
\end{itemize}

\subsection*{Senior Software Engineer, PTC Schweiz (Zürich and Remote EU - Romania) \hfill Oct 2015 - Jan 2024}
\begin{itemize}
  \item Built, owned and operated Vuforia Cloud microservices (Scala, Akka) for manufacturing Augmented Reality products LIVE on AWS.
  \item Collaborated strongly with Machine Learning engineering Team to integrate models into production APIs and containerized services; collaborated with testing and support teams.
  \item Implemented end-to-end automated tests in Scala to strengthen the reliability of REST APIs reducing on-call incidents.
  \item Developed CI/CD pipelines with GitHub Actions and TeamCity.
  \item Delivered major refactors and contributed to internal deployment tooling.
  \item Led initiatives to develop internal tools that improved developer productivity across multiple teams.
  \item Integrated static analysis tools like Veracode and Snyk into the development workflow to enhance code security and quality.
  \item Implemented security best practices across services after completing multiple security training programs throughout the years (owasp, remote).
  \item Implemented Single Sign On auth with Amazon Cognito.
  \item Contributed to monitoring and observability initiatives (Elasticsearch, Logstash, Kibana).
  \item Authored API documentation using OpenAPI v3.
  \item Implemented WebSocket (proxy) service for real-time collaboration services app (remote assistance, Chalk).
  \item Conducted technical interviews and contributed to engineering hiring decisions.
\end{itemize}

\subsection*{Senior Engineer, Qualcomm (Zürich, Switzerland) \hfill Jan 2014 - Oct 2015}
\begin{itemize}
  \item Expanded cloud services with Scala and Play on AWS.
  \item Automated operations and built internal tools tasks using Python and Bash.
  \item Ported services to Docker and maintained legacy Ruby on Rails systems.
  \item Designed and built an internal Ruby DSL for testing APIs across multiple teams, collaborating closely with those teams.
  \item Participated in scaling infrastructure from a few to hundreds of EC2 instances on AWS (S3, SQS, DynamoDB, Cognito, Autoscaling).
\end{itemize}

\subsection*{Software Engineer, Kooaba (Zürich, Switzerland) \hfill Feb 2011 - Jan 2014}
\begin{itemize}
  \item Initiated and led the move from a monolith to Scala-based microservices, increased scalability and reduced memory usage.
  \item Built REST APIs and a web backend using Ruby on Rails.
  \item Rewrote and maintained an Android application.
  \item Performed MySQL optimizations/ updates on live databases with 30m+ rows.
\end{itemize}

\subsection*{Head of Technology, Alliants (Cluj-Napoca, Romania) \hfill Sep 2008 - Feb 2011}
\begin{itemize}
  \item Hired and led a small team of 3 engineers delivering Ruby on Rails apps for different customers.
  \item Coordinated on-site delivery in London.
\end{itemize}

\section*{Skills}
\begin{itemize}
  \item Languages: Ruby, Python, Scala, JavaScript, Bash
  \item Frameworks and Libraries: Rails, Akka, Play, Node.js
  \item Cloud and Infrastructure: AWS, GCP, Docker, REST APIs, Oauth2, JWT, SSO
  \item Data and Search: MySQL, Elasticsearch, Kibana
  \item Testing and Tooling: GitHub Actions, TeamCity, LaTeX, Open API, linux, awk, sed
\end{itemize}

\section*{Education}
\begin{itemize}
  \item Master's Degree, Computer Science --- Babes-Bolyai University, Cluj-Napoca (2008--2010). Thesis: Recommender Systems using Collaborative Filtering (\href{https://github.com/christian/Rho-article}{https://github.com/christian/Rho-article}).
  \item Bachelor's Degree, Computer Science --- Alexandru Ioan Cuza University, Iasi (2005--2008). Thesis: Mobile Recommender System.
  \item Machine learning course, with Andrew Ng.
  \item Back in 2011, before Coursera was invented.
\end{itemize}

\section*{Languages}
English (fluent), Romanian (fluent), German (basic), French (basic)

\section*{Fun projects}
\begin{itemize}
  \item I love music. Since 2013 I'm building and evolving a Virtual Private Organ (musical instrument). Here's the initial story: \href{hauptwerk/virtual-private-organ.html}{hauptwerk/virtual-private-organ.html}. Some Arduino programming on my github: \href{https://github.com/christian/virtual-organ/tree/master/ArduinoCombinationPistons}{https://github.com/christian/virtual-organ/tree/master/ArduinoCombinationPistons}.
  \item In 2025, I conducted a small Christmas concerto with our small choir and orchestra.
  \item I'm a big fan of LilyPond for engraving sheet music: \href{https://lilypond.org/}{https://lilypond.org/}.
  \item Bootstrapped and maintained e-commerce solution featuring various API integrations LIVE since 2012: \href{https://www.perlasuferintei.ro/}{https://www.perlasuferintei.ro/}.
\end{itemize}

\end{document}
